---
title: "Introduction"
author: "Dookyung Kim"
date: "2018-05-06"
output:
  xaringan::moon_reader:
    css: "slides.css"
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

exclude: true

```{r, message=FALSE, warning=FALSE, include=FALSE}
# R options
options(
  htmltools.dir.version = FALSE, # for blogdown
  show.signif.stars = FALSE,     # for regression output
  warm = 1
  )
# Set dpi and height for images
library(knitr)
opts_chunk$set(fig.height = 2.65, dpi = 300) 
# ggplot2 color palette with gray
color_palette <- list(gray = "#999999", 
                      salmon = "#E69F00", 
                      lightblue = "#56B4E9", 
                      green = "#009E73", 
                      yellow = "#F0E442", 
                      darkblue = "#0072B2", 
                      red = "#D55E00", 
                      purple = "#CC79A7")
# For nonsese...
# library(emo)
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(rvest)
```

---

class: center, middle

# Hello world!

---

class: .big

## What is data science?


--
- <i class="fa fa-database fa-10x"></i> + <i class="fa fa-flask fa-10x"></i> = data science?

--

- <i class="fa fa-database fa-10x"></i> + <i class="fa fa-code fa-10x"></i> = data science?

--

- <i class="fa fa-database fa-10x"></i> + <i class="fa fa-user fa-10x"></i> + <i class="fa fa-code fa-10x"></i> = data science?

--

- <i class="fa fa-database fa-10x"></i> + <i class="fa fa-users fa-10x"></i> + <i class="fa fa-code fa-10x"></i> = data science?

--

<br>

원시데이터(raw data)부터 세상의 현상이나 이치 대한 이해(understanding), 통찰(insight), 지식(knowledge)을 도출하는 학문

R을 활용하여 보다 tidy way한 방식으로... 

---
# What is this course?

Everything you will need for the course will be posted at

[dkkim-r4ds.netlify.com/](https://dkkim-r4ds.netlify.com/)

--

- Will we be doing computing? Yes.

--

- Is this an intro CS course? No, but many themes are shared.

--

- Is this an intro stat course? Yes, but it's not your high school statistics course.

--

- What computing language will we learn? R.

--

- Why not language X? We can discuss that over <i class="fa fa-coffee"></i> .

